---
output:
  md_document:
    variant: markdown_github
---
# playground4litedown

This repo exists because of [this toot in mastodon](https://mastodon.social/@defuneste@fosstodon.org/113398806612007032) requesting help to build a small [{litedown}](https://github.com/yihui/litedown) site.

## Installation

```{r echo=TRUE, eval=FALSE, include=TRUE}
pak::pak(c("yihui/litedown", "yihui/servr"))
```

## Example

I list multiple options here:

* Render the site from one place, and serve it from another place.

```{r echo=TRUE, eval=FALSE, include=TRUE}
litedown::fuse_site("www1")
from_files <- c(
  fs::dir_ls("www1/src", glob = "*.html"),
  fs::dir_ls("www1/src", glob = "*_files")
)
fs::file_move(from_files, "www1")
servr::httw("www1", ".", handler = \(x) {
    cat(paste(x), " changed", '\n')
    litedown::fuse_site(".")
    from_files <- c(
      fs::dir_ls("src", glob = "*.html"),
      fs::dir_ls("src", glob = "*_files")
    )
    fs::file_move(from_files, ".")
})
```


* Render the site and serve it from the same place, watching for changes to re-render.

```{r echo=TRUE, eval=FALSE, include=TRUE}
litedown::fuse_site("www2")
servr::httw("www2", ".", handler = \(x) {
    cat(paste(x), " changed", '\n')
    litedown::fuse_site(".")
})
```

* Launch a web page to list and preview R Markdown and HTML files under the same directory.

```{r}
litedown::fuse_site("www3")
litedown::roam("www3") 
```
